NGO Repression as a Predictor of Worsening Human Rights Abuses

### 2021-11-17 manuscript/manuscript.Rmd
Add @

This trend holds across many other countries as well. For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented. Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [Chaudhry:2022]. Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.

>>>>

This trend holds across many other countries as well. For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented. Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [@Chaudhry:2022]. Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.
